Which Amazon Problem? Problem-constructions and Transnationalism in Brazilian

### 2023-02-18 Submission/Re-submission/draft/draft_resubmission_shorten.rmd
final
submission documents

---
title: "Which Amazon Problem? Problem-constructions and Transnationalism in Brazilian
  Presidential Discourse since 1985"
author:
- "Livio Silva-Muller"
- Henrique Sposito^[Both authors contributed equally to the article. Names are ordered
  alphabetically. Livio is a PhD Candidate in Sociology and affiliated to the Albert
  Hirschman Centre on Democracy. Henrique is a PhD Candidate in International Relations
  and Political Sciences and affiliated to the Centre for International Environmental
  Studies.]
date: "17 February 2023"
output:
  pdf_document: default
  latex_engine: xelatex
  fig_caption: yes
  html_document:
    df_print: paged
  word_document: default
fontsize: 12pt
mainfont: Times New Roman
header-includes:
- \usepackage{floatrow}
- \floatsetup[figure]{capposition=top}
- \usepackage{float}
- \floatplacement{figure}{H}
- \usepackage[T1]{fontenc}
- \usepackage[utf8]{inputenc}
- |
  \providecommand{\keywords}[1]{\textbf{Keywords:} #1}
  \providecommand{\wordcount}[1]{\textbf{Word Count:}#1}
always_allow_html: yes
bibliography: references.bib
csl: chicago.csl
abstract: The Amazon is a complex object of policy that comprises environmental, economic, social, and sovereignty concerns. Despite this complexity, governments are often portrayed as having a single understanding of the region as a political problem. In this article, we investigate how the Amazon has been constructed as a problem in Brazilian presidential speeches since 1985.To do so, we develop a framework that accounts for how important transnational actors, as presidents, construct policy objects as particular problems depending on where and when they participate in politics. We find that presidents often construct the Amazon as an environmental problem when speaking far away from the region, whereas they usually construct it as problems of economic integration or social development when in the Amazon. Furthermore, presidents are increasingly more likely to mix problem-constructions and construct the Amazon as a complex and multifaceted object of policy.
---

@@

# Introduction

@@

# 5 Conclusion

@@

# Acknowledgements

The authors are extremely grateful to Graziella Moraes Silva, James Hollway, and Matias López for their support. The authors would also like to thank the anonymous reviewers, Anna, Federico, Mario, and Rodrigo for their invaluable help.

>>>>

---
title: "Which Amazon Problem? Problem-constructions and Transnationalism in Brazilian
  Presidential Discourse since 1985"
author:
- "Livio Silva-Muller"
- Henrique Sposito^[Both authors contributed equally to the article. Names are ordered
  alphabetically. Livio is a PhD Candidate in Sociology and affiliated to the Albert
  Hirschman Centre on Democracy. Henrique is a PhD Candidate in International Relations
  and Political Sciences and affiliated to the Centre for International Environmental
  Studies.]
date: "17 February 2023"
output:
  pdf_document: default
  latex_engine: xelatex
  fig_caption: yes
  html_document:
    df_print: paged
  word_document: default
fontsize: 12pt
mainfont: Times New Roman
header-includes:
- \usepackage{floatrow}
- \floatsetup[figure]{capposition=top}
- \usepackage{float}
- \floatplacement{figure}{H}
- \usepackage[T1]{fontenc}
- \usepackage[utf8]{inputenc}
- |
  \providecommand{\keywords}[1]{\textbf{Keywords:} #1}
  \providecommand{\wordcount}[1]{\textbf{Word Count:}#1}
always_allow_html: yes
bibliography: references.bib
csl: chicago.csl
abstract: The Amazon is a complex object of policy that comprises environmental, economic, social, and sovereignty concerns. Despite this complexity, governments are often portrayed as having a single understanding of the region as a political problem. In this article, we investigate how the Amazon has been constructed as a problem in Brazilian presidential speeches since 1985.To do so, we develop a framework that accounts for how important transnational actors, as presidents, construct policy objects as particular problems depending on where and when they participate in politics. We find that presidents often construct the Amazon as an environmental problem when speaking far away from the region, whereas they usually construct it as problems of economic integration or social development when in the Amazon. Furthermore, presidents are  increasingly mixing problem-constructions and constructing the Amazon as a complex and multifaceted object of policy.
---

@@

# 1. Introduction

@@

# 5. Conclusion

@@
